### 2022-01-14 acks.tex
new approach section
fixes that james wanted
fixes
fix samie's name

\section*{Acknowledgements}\label{sec:acks}
\todo[inline]{TODO: James? Funding? Project course students?}

>>>>

\section*{Acknowledgements}\label{sec:acks}

This research has been partially funded by
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; and }}]
    \item the VINNOVA Competence Center for \ac{TECoSA} at KTH Royal Institute of Technology
    \item the \ac{SSF}, through grant number ITM17--0246.
\end{enumerate*}

We also wish to thank S.~S.~Mostafavi, V.~N.~Moothedath, M.~Alsakati, O.~Ferm, S.~Vojcic, and A.~Bhattacharya for their support and valuable contributions to this work.
